Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2018-01-09 paper/paper.Rmd
Formatted digits in regression table to all have two decimal places

ModelEstimatesTable <- as.data.frame(cbind(ModelEstimatesTypes, ModelEstimatesSign[,2:5])) %>%
mutate(A = ifelse(A.s=="   ", "-", A.e),
       G = ifelse(G.s=="   ", "-", G.e),
       M = ifelse(M.s=="   ", "-", M.e),
       S = ifelse(S.s=="   ", "-", S.e))%>% 
  # unite(Animetrics, A, A.s, sep="") %>% 
  # unite(Google, G, G.s, sep="") %>% 
  # unite(Microsoft, M, M.s, sep="") %>% 
  # unite(Skybiometry, S, S.s, sep="") %>%
  # select(variable, Animetrics, Google, Microsoft, Skybiometry)
  mutate(` ` = A.s,
         `  ` = G.s,
         `   ` = M.s,
         `    ` = S.s) %>%
   select(variable, A, ` `,
          G, `  `, 
          M, `   `,
          S, `    `)

knitr::kable(ModelEstimatesTable, format = "latex", align=c("l", 
                                          "r", "l",
                                          "r", "l",
                                          "r", "l",
                                          "r", "l"),
             booktabs = TRUE, longtable=FALSE, caption="Evaluation of factors affecting face recognition for API, as assessed by logistic regression model. Coefficients from the four models shown (significance: ** 0.01 * 0.05 . 0.01 - NS). Most APIs wre affected by similar factors, with glasses, visor or hat, head angle, lighting, shot angle and situation all contributing significantly to face detection.")
```

*** The number of digits should be consistent, e.g. "-1" should be "-1.00". I don't know how to force this with the kale printing, but one way or another we have to.

>>>>

ModelEstimatesTable <- as.data.frame(cbind((ModelEstimatesTypes), ModelEstimatesSign[,2:5])) %>%
mutate(A = ifelse(A.s=="   ", "-", format(round(A.e, 2), nsmall = 2)),
       G = ifelse(G.s=="   ", "-", format(round(G.e, 2), nsmall = 2)),
       M = ifelse(M.s=="   ", "-", format(round(M.e, 2), nsmall = 2)),
       S = ifelse(S.s=="   ", "-", format(round(S.e, 2), nsmall = 2))) %>% 
  select(variable, A, ` ` = A.s,
         G, `  ` = G.s,
         M, `   ` = M.s,
         S, `    ` = S.s)

knitr::kable(ModelEstimatesTable, format = "latex", align=c('l', 
                                           'r', 'l',
                                           'r', 'l',
                                           'r', 'l',
                                           'r', 'l'),
             booktabs = TRUE, longtable=FALSE, caption="Evaluation of factors affecting face recognition for API, as assessed by logistic regression model. Coefficients from the four models shown (significance: ** 0.01 * 0.05 . 0.01 - NS). Most APIs wre affected by similar factors, with glasses, visor or hat, head angle, lighting, shot angle and situation all contributing significantly to face detection.")
```
